Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-25 GWLDCII.tex
fixed the cite

As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope.  Each of these individual integrals have singularities which come from the factors in the denominator of the integrands. However, SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}, so the singularities must cancel out in the sum over all diagrams. This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{GWLDCI}.

>>>>

As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope.  Each of these individual integrals have singularities which come from the factors in the denominator of the integrands. However, SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}, so the singularities must cancel out in the sum over all diagrams. This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.
